---
title: 'Project: Model Evaluation and Deployment'
author: "Meghana Nerusu"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
library(tidyverse)
library(dplyr)
library(rpart)
library(rpart.plot)
```

## Data Cleaning 

```{r}
advise_invest_clean <- read_csv("adviseinvest.csv", show_col_types = FALSE)  %>%            # Download data
  select(-product) %>%                                        # Remove the product column
  na.omit %>%                                                 # Remove NAs
  filter(income > 0,                                          # Filter out mistaken data
         num_accts < 5) %>% 
  mutate(answered = factor(ifelse(answered==0, "no","yes"),   # Turn answered into yes/no factor
                           levels  = c("no", "yes")),
         female = factor(female),                             # Make categorical variables into factors
         job = factor(job),
         rent = factor(rent),
         own_res = factor(own_res),
         new_car = factor(new_car),
         mobile = factor(mobile),
         chk_acct = factor(chk_acct),
         sav_acct = factor(sav_acct)) 
advise_invest_clean

customer_data_clean <- read_csv("customer_data.csv", show_col_types = FALSE) %>% 
  mutate(female = factor(female),
         job = factor(job),
         rent = factor(rent),
         own_res = factor(own_res),
         new_car = factor(new_car),
         mobile = factor(mobile),
         chk_acct = factor(chk_acct),
         sav_acct = factor(sav_acct)) 

```


### How does the decision tree model classify customers, and how accurate are its predictions?

```{r}
tree_model_a <- rpart(formula = answered ~., data = advise_invest_clean)
table(predicted = predict(tree_model_a, type = "class"),
observed = advise_invest_clean$answered)
```

### What is the cost-benefit analysis, and how does it help evaluate the model's performance?

```{r}
Values<-list(c("predicted yes", "predicted no"),c("observed yes", "observed no"))
costbenefit_matrix <- matrix(c(75,0,-25,0), ncol = 2, dimnames = Values)
costbenefit_matrix
13820*75-3008*25
```

### Calculate the net benefit matrix
```{r}
(13820+2304)*75 - (10367+3008)*25
```

### How does adjusting the decision threshold affect model outcomes and business decisions
```{r}
tree_model_a <- rpart(formula = answered ~., data = advise_invest_clean)
table(predicted = ifelse(predict(tree_model_a, type = "prob")[,2] >= .3, "YES", "NO"),
      observed = advise_invest_clean$answered)

14268*75-3776*25

```

### How are the model's predictions applied to a new dataset, and what does it reveal about potential customer churn?

```{r}
predict(tree_model_a, 
        data = customer_data_clean, 
        type = "prob") [ ,2] %>% 
  head(25)

glimpse(customer_data_clean)

customercontacts <- customer_data_clean %>% 
  select(customer_id) %>% 
  mutate(churn = predict(tree_model_a, 
        newdata = customer_data_clean, 
        type = "prob") [ ,2]) %>%
  filter(churn>=0.3)

glimpse(customercontacts)
```



